Error SDE ($Z_t$) moments

### 2020-04-03 MATLAB_Files/MATLAB_readMe/MATLAB_readMe.tex
The file moments_verification_Lamperti.e seems to be working almost correctly. I noticed that in the SDE for the second moment, it was necessary a sqrt(). However, now we need to choose another Lamp. Transform, because of this square root.
The moments seem to be working well.

@@

\end{itemize}
\quad\\
\quad\\
They have the same partial derivatives. The main difference appears in the resulting SDE for $Z_t$.\\
\quad\\
For now, we will use the {\color{blue}first candidate}.

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Lamperti moments:}

The Lamperti SDE is:
\begin{align*}
\dif Z_t= \underbrace{\left[  \frac{(\alpha \theta_0 - \theta_t) {\color{black}\sin(\sqrt{2 \alpha \theta_0 } Z_t) }- \theta_t (1 - 2 p_t) + 2  \dot{p}_t }{\sqrt{2 \alpha \theta_0} \cos{(\sqrt{2 \alpha \theta_0} Z_t)}}  \right]}_{\coloneqq b(Z_t)} \dif t + \dif W_t . 
\end{align*}
Here we follow Bayesian Filtering and Smoothing, Chapter 9. We use the linearization-based approximation for the moments.\\
\quad\\
As $X_t\in(\alert{0},1)$, we have that $Z_t\in\left(\alert{-\frac{\pi}{2}\frac{1}{\sqrt{2\alpha\theta_0}}},\frac{\pi}{2}\frac{1}{\sqrt{2\alpha\theta_0}}\right)$.

@@

\begin{equation*}
\begin{cases}
\dif \sigma^2_L(s)&=\left(2\sigma^2_Lb'(\mu_L(s))+1\right)\dif s,\\
\sigma^2_L(t_{n-1})&=0.
\end{cases}
\end{equation*}
\quad\\
We solve numerically the ODE using Forward-Euler:
\begin{equation*}
\sigma^2_L(s_{n})=\sigma^2_L(s_{n-1})+\left(1+2\sigma^2_L(s_{n-1})b'(\mu_L(s_{n-1}))\right)\Delta s.
\end{equation*}
We have that (computed with Mathematica):
\begin{equation*}
b'(z)=\frac{\dif b}{\dif z}(z)=\frac{\alpha\theta_0-\theta_t+(2\dot{p}_t+(2p_t-1)\theta_t)\sin(z\sqrt{2\alpha\theta_0}))}{\cos^2(z\sqrt{2\alpha\theta_0})}.
\end{equation*}

>>>>

\item I had to add an artificial correction to ensure that the second moment is always positive. It is in function log\_LH\_evaluation.m.

@@

\end{itemize}
\quad\\
\quad\\
They have the same partial derivatives. The main difference appears in the resulting SDE for $Z_t$.\\
\quad\\
For now, we will use the {\color{red}second candidate}. The problem with the {\color{blue} first candidate} is that the mapping $Z_t\to Z_t^2$ is not injective.

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Lamperti SDE: {\color{blue} first candidate} (this slide may be deleted so soon...)}

The Lamperti SDE is:
\begin{align*}
\dif Z_t= \underbrace{\left[  \frac{(\alpha \theta_0 - \theta_t) {\color{black}\sin(\sqrt{2 \alpha \theta_0 } Z_t) }- \theta_t (1 - 2 p_t) + 2  \dot{p}_t }{\sqrt{2 \alpha \theta_0} \cos{(\sqrt{2 \alpha \theta_0} Z_t)}}  \right]}_{\coloneqq b(Z_t)} \dif t + \dif W_t . 
\end{align*}
Here we follow Bayesian Filtering and Smoothing, Chapter 9. We use the linearization-based approximation for the moments.\\
\quad\\
As $X_t\in(\alert{0},1)$, we have that $Z_t\in\left(\alert{-\frac{\pi}{2}\frac{1}{\sqrt{2\alpha\theta_0}}},\frac{\pi}{2}\frac{1}{\sqrt{2\alpha\theta_0}}\right)$.
{
Also, we have that (computed with Mathematica):
\begin{equation*}
b'(z)=\frac{\dif b}{\dif z}(z)=\frac{\alpha\theta_0-\theta_t+(2\dot{p}_t+(2p_t-1)\theta_t)\sin(z\sqrt{2\alpha\theta_0}))}{\cos^2(z\sqrt{2\alpha\theta_0})}.
\end{equation*}}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Lamperti SDE: {\color{red} second candidate}}

The Lamperti SDE is:
\begin{align*}
\dif Z_t= \underbrace{\left[\frac{\alpha\theta_0\cos(Z_t\sqrt{2\alpha\theta_0})-\theta_t\cos(Z_t\sqrt{2\alpha\theta_0})+2\theta_tp_t+2\dot{p}_t-\theta_t}{\sqrt{\alpha\theta_0}\sqrt{1-\cos(2Z_t\sqrt{2\alpha\theta_0})}}\right]}_{\coloneqq b(Z_t)} \dif t + \dif W_t . 
\end{align*}
Here we follow Bayesian Filtering and Smoothing, Chapter 9. We use the linearization-based approximation for the moments.\\
\quad\\
As $X_t\in(\alert{0},1)$, we have that $Z_t({\color{blue}[0},\alert{1]})={\color{blue}\Big[\frac{-\pi}{\sqrt{2\alpha\theta_0}}},\alert{0\Big]}$.
{
Also, we have that (computed with Mathematica):
\begin{equation*}
b'(z)=\frac{\dif b}{\dif z}(z)=-\frac{\alpha\theta_0-\theta_t+\cos(\sqrt{2\alpha\theta_0}z)(2\dot{p}_t+\theta_t(2p_t-1))}{\left(\sin(\sqrt{2\alpha\theta_0}z)\right)^2}.
\end{equation*}}

@@

\begin{equation*}
\begin{cases}
\dif \sigma^2_L(s)&=\left(2\sigma^2_Lb'(\mu_L(s))+1\right)\dif s,\\
\sigma^2_L(t_{n-1})&=0.
\end{cases}
\end{equation*}
\quad\\
We solve numerically the ODE using Forward-Euler:
\begin{equation*}
\sigma^2_L(s_{n})=\sigma^2_L(s_{n-1})+\left(1+2\sigma^2_L(s_{n-1})b'(\mu_L(s_{n-1}))\right)\Delta s.
\end{equation*}

### 2020-04-03 Reports/20200403 - Moments_all/20200403 - Moments_all.tex
The moments seem to be working well.

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Introduction:} \label{S1}

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated first moment for $Z_t$:}

@@

>>>>

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Data histograms:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/histograms/others/forecast_transitions.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/histograms/others/error_measurement.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/histograms/others/error_and_forecast.eps}
\end{figure}
From here we can see that the error transitions are approximately in the interval $[-0.3,0.3]$, and the forecast transitions in the interval $[-0.03,0.03]$.\\
Then, we want to ensure that the moments are well approximated in the rectangle $[-0.3,0.3]\times[-0.03,0.03]$ (for $\Delta V\times\Delta p$).

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated moments for $Z_t$:}

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated moments for $Z_t$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/moments/lamperti/7.eps}
\end{figure}
